Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-07 Paper/Poster/poster.tex
better

\usepackage{epsfig}
\usepackage{multicol}
\usepackage{pstricks,pst-grad}
\usepackage{url}
\usepackage{wrapfig}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Availability of very large collections of music audio:
can we infer anything about the underlying structure and common
features of e.g. commercial pop music?
\item Our interest: tonal content of the music -- i.e. the
harmony and melody.
\item Beat-synchronous chromagrams: rich enough
to generate musically-relevant results, simplified enough to
abstract away instrumentation and other stylistic details.
\item This paper identifies common patterns in beat-synchronous
chromagrams by learning codebooks from a large set of examples.
The individual codewords consist of short beat-chroma patches of
between 1 and 8 beats, optionally aligned to bar boundaries.
\end{list}

@@

%
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Goal: identify meaningful information
about the musical structure represented in the entire database by
examining individual entries in this codebook.
\item Prior work: ``shingles'' of \cite{Casey2007}, 
beat-synchronous analysis to indeitfy the chorus by \cite{Bartsch2001},
and cover recognition by \cite{Ellis2007a}.
\end{list}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item A bullet point
\item A bullet point
\item A bullet point
\end{list}

@@

@@

%%% References
\bibliographystyle{IEEEtran}
\bibliography{tbm_bib}

>>>>

\usepackage{epsfig}
\usepackage{multicol}
\usepackage{pstricks,pst-grad}
\usepackage{url}
\usepackage{wrapfig}
\usepackage{algorithm,algorithmic}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Availability of very large collections of music audio:
can we infer anything about the underlying structure and common
features of e.g. commercial pop music?
\item Our interest: tonal content of the music -- i.e. the
harmony and melody.
\item Beat-synchronous chromagrams: rich enough
to generate musically-relevant results, simplified enough to
abstract away instrumentation and other stylistic details.
\end{list}

@@

%
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Goal: identify meaningful information
about the musical structure represented in the entire database by
examining individual entries in this codebook.
\item Method: identify common patterns in beat-synchronous
chromagrams by learning codebooks from a large set of examples.
Individual codewords consist of short beat-chroma patches of
between 1 and 8 beats, optionally aligned to bar boundaries.
\item Prior work: ``shingles'' of \cite{Casey2007}, 
beat-synchronous analysis to indeitfy the chorus by \cite{Bartsch2001},
and cover recognition by \cite{Ellis2007a}.
\end{list}

@@

\textbf{Chromagrams from the Echo Nest online API.}
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Feature analysis based on Echo Nest analyze API \cite{EchoNest}.
\item For any song, EchoNest provides a chroma
vector (length $12$) for every music event (called ``segment''), and a
segmentation of the song into beats and bars. Beats may span or 
subdivide segments; bars span multiple beats.
\item Averaging per-segment chroma over beat times results in a
beat-synchronous chroma feature representation.
\item Dataset size: $43,000$ songs.
\end{list}

\textbf{Beat-Chroma Patches.}
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item We use Echo Nest analysis to break a song into a collection of 
beat-chroma ``patches'', typically one or two bars in length.
\item $82\%$ of the bars in our data were 4 beats long.
\item Other cases: we resample patches to a fixed length of 4 beats.
\item We rotate patches so that the first row contains the most energy.
Each patch is normalized independently.
\end{list}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Vector Quantization algorithm \cite{Gersho1991} to cluster beat-chroma
patches
\item VQ can be seen as online $k$-means
\item VQ initialized with $k$ random patches from the data
\item VQ, although not optimal, scales linearly with
the number of patches seen
\end{list}

\begin{minipage}{\columnwidth}
%\caption{Pseudocode of Vector Quantization}
\begin{algorithmic}
\begin{algorithm}[H]
\STATE$\ell$ learning rate
\STATE$\{P_n\}$ set of patches
\STATE$\{C_k\}$ codebook of $K$ codes
\REQUIRE $0 < \ell \leq 1$
\FOR{$nIters$}
\FOR{$p \in \{P_n\}$}
\STATE{$c \leftarrow \min_{c \in C_k} \mbox{dist}(p,c)$}
\STATE{$c \leftarrow c + (p - c) * \ell$}
\ENDFOR
\ENDFOR
\RETURN $\{C_k\}$
\end{algorithm}
\end{algorithmic}
\end{minipage}

@@

%%% References
\begin{small}
\bibliographystyle{IEEEtran}
\bibliography{tbm_bib}
\end{small}
